A Loop Quantm Gravity Inspired Action for the Bosonic String and Emergent Dimensions at Large Scales

### 2025-07-05 AoP/response-to-referee.tex

\emph{However, our construction differs from standard AdS/CFT in several important ways: (1) it emerges at the classical level from gauge theory requirements rather than from quantum/non-perturbative effects, (2) the holographic direction arises from the string action itself rather than being an external bulk geometry, and (3) the correspondence is between worldsheet dynamics and the extended embedding space rather than between a boundary CFT and bulk gravity. While this provides a concrete classical realization of holographic principles, establishing a precise correspondence with Maldacena's duality would require demonstrating how our construction reproduces the specific correlation functions and scaling behaviors characteristic of AdS/CFT, which remains an open challenge for future work.}

\subsection{Discussion - Part (a): Open Questions}

\RC The discussion synthesizes the paper's key results but could better highlight open questions (e.g., experimental signatures, relation to black hole physics), considering the ideas established in the manuscript.

\AR Following the referee's suggestion we have added the following paragraph right after eq (7.12), relating the cosmological constant $\Lambda$ and the deSitter length $l$:

\emph{Given the observed cosmological constant $\Lambda \approx 1.47 \times 10^{-52} \text{m}^{-2}$ \citep{Collaboration2020Planck}, eq (7.12) implies that $l \approx 1.4 \times 10^{26} \text{m}$. This happens to coincide with the scale of the cosmological horizon \citep{Peebles2003Cosmological}. This would suggest that the scale of the emergent dimension $X^r$ is of the order of the cosmological horizon. Of course, this is a very naive ``back of the envelope'' calculation and would require further investigation to place on a firmer footing.}

@@

\subsection{Discussion - Part (b): Anomaly-Free and Ghost-Free Claims}

\RC The claim that the model is anomaly-free and ghost-free (Sec. 5) should be tempered with caveats (e.g., limitations of the truncation scheme).

\AR We agree with the referee's assessment. We have added the following paragraph following the paragraphs discussing the limitations of our ``anomaly free'' claims (which were also added in response to points raised by the referee):

\emph{Additionally, our anomaly-freedom and ghost-freedom analysis is limited to the tree-level constraints; quantum loop corrections and the full quantum effective action may introduce subtleties not captured in this treatment.}

### 2025-07-05 lqg-strings.tex
feat: T2 - Complete AOP reviewer responses for Sections 7 and 8.
- Discussion section enhancements with cosmological horizon connection and experimental signatures
- T2 finished, only overall review for typos and grammar required
- Updated memory bank

@@

This is where the non-zero value of $\ep$ mentioned in \eqref{eqn:poincare-lie-algeba} come into play. It turns out that for $\ep = +1$ ($\ep = -1$) the connection in \eqref{eqn:poincare-lie-algeba} describes a $\mf{so}(4,1)$ ($\mf{so}(3,2)$) connection respectively. These describe the symmetries of (asymptotically) deSitter and anti-deSitter spacetimes respectively. The length scale $l$ determines the value of the effective cosmological constant in the dS (adS) geometries:
\begin{equation}\label{eqn:cosmological-constant}
	\lambda = \frac{3 \ep}{l^2}.
\end{equation}
One might ask what is the motivation for introducing dS (adS) geometries into the discussion. The main motivation of course is the Maldacena or adS/CFT correspondence. The adS spacetime is usually understood to arise as a consequence of non-perturbative effects which nobody really has a proper understanding of as yet. One might hope that for a correspondence which has passed all possible checks uptil now, there should be some way to realise it in the classical theory also.

@@

>>>>

Additionally, our anomaly-freedom and ghost-freedom analysis is limited to the tree-level constraints; quantum loop corrections and the full quantum effective action may introduce subtleties not captured in this treatment.

@@

This is where the non-zero value of $\ep$ mentioned in \eqref{eqn:poincare-lie-algeba} come into play. It turns out that for $\ep = +1$ ($\ep = -1$) the connection in \eqref{eqn:poincare-lie-algeba} describes a $\mf{so}(4,1)$ ($\mf{so}(3,2)$) connection respectively. These describe the symmetries of (asymptotically) deSitter and anti-deSitter spacetimes respectively. The length scale $l$ determines the value of the effective cosmological constant in the dS (adS) geometries:
\begin{equation}\label{eqn:cosmological-constant}
	\Lambda = \frac{3 \ep}{l^2}.
\end{equation}
Given the observed cosmological constant $\Lambda \approx 1.47 \times 10^{-52} \text{m}^{-2}$ \cite{Collaboration2020Planck}, eq \eqref{eqn:cosmological-constant} implies that $l \approx 1.4 \times 10^{26} \text{m}$. This happens to coincide with the scale of the cosmological horizon \cite{Peebles2003Cosmological}. This would suggest that the scale of the emergent dimension $X^r$ is of the order of the cosmological horizon. Of course, this is a very naive ``back of the envelope'' calculation and would require further investigation to place on a firmer footing.

One might ask what is the motivation for introducing dS (adS) geometries into the discussion. The main motivation of course is the Maldacena or adS/CFT correspondence. The adS spacetime is usually understood to arise as a consequence of non-perturbative effects which nobody really has a proper understanding of as yet. One might hope that for a correspondence which has passed all possible checks uptil now, there should be some way to realise it in the classical theory also.

@@

\subsection{Open Questions and Future Directions}\label{sec:open-questions}

While our work establishes a promising framework for incorporating LQG insights into string theory, several fundamental questions remain open. Building on the pioneering work of Smolin \cite{Smolin1998Strings} and Markopoulou \cite{Markopoulou1997Causal}, a more complete framework is needed to show how smooth worldsheet geometries emerge from the discrete, punctured surfaces of spin networks in Loop Quantum Gravity. Our earlier work \cite{Vaid2017Connecting} established that the Nambu-Goto action can be viewed as the expectation value of the LQG area operator, but the detailed emergence mechanism requires further development.

The physical interpretation of the emergent holographic dimension $X^r$ also requires further study. Understanding the physical nature of this dimension and its emergence mechanism represents a key theoretical challenge, though the connection to Afshordi's model provides important guidance.

Perhaps most significantly, the relationship between our modified constraint algebra and the fundamental structure of spacetime at the Planck scale requires clarification. Do the two-index Virasoro generators correspond to a deeper geometric principle? Can they be understood by some suitable deformation of the Virasoro algebra to incorporate the cutoff of the sum over Virasoro modes?
